---
<<<<<<< HEAD
title: "RepData assesment1"
author: "kessoku"
date: "Monday, December 08, 2014"
output: html_document
---

Loading and preprocessing the data
```{r, echo=TRUE}
data <- read.csv("./repdata-data-activity/activity.csv")
```

the plot of total number of steps taken each day is
```{r, echo=TRUE}
library(ggplot2)
data.nonNA <- data[ which( is.na( data[,"steps"] ) == FALSE ), ]

steps.by.date <- tapply(data.nonNA$steps, data.nonNA$date, sum)
ggplot( data.frame(steps.by.date), aes(steps.by.date)) + geom_histogram()
```

the mean and median total number of steps taken per day are
```{r, echo=TRUE}
tapply(data.nonNA$steps, data.nonNA$date, mean)
tapply(data.nonNA$steps, data.nonNA$date, median) 
```

the average daily activity pattern is 
```{r, echo=TRUE}
intSteps.per.date <- tapply(data.nonNA$steps, data.nonNA$interval, mean)
plot( x=names(intSteps.per.date), y=intSteps.per.date, type="l", xlab="interval", ylab="steps")
```

the maximum number of steps is 
```{r, echo=TRUE}
max(intSteps.per.date)
names( intSteps.per.date[which( intSteps.per.date==max(intSteps.per.date) )] )
```

the num. of missing values is 
```{r, echo=TRUE}
sum( is.na( data$steps ) == TRUE )
```

the plot of dataset with the missing data filled in is 
```{r, echo=TRUE}
data.imputeNA <- data
NA.row.index <- which( is.na( data.imputeNA$steps ) == TRUE )
data.imputeNA[ NA.row.index, 1] <- 
  sapply( data.imputeNA[ NA.row.index, 3 ], 
          function(x){ intSteps.per.date[ which( names(intSteps.per.date) == x ) ]  } )

steps.by.date.2 <- tapply(data.imputeNA$steps, data.imputeNA$date, sum)
ggplot( data.frame(steps.by.date.2), aes(steps.by.date.2)) + geom_histogram()
```

the mean and median total number of steps taken per day are
```{r, echo=TRUE}
tapply(data.imputeNA$steps, data.imputeNA$date, mean)
tapply(data.imputeNA$steps, data.imputeNA$date, median) 
```


Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
weekday.end <- 
data.frame( sapply( weekdays( as.Date(data.imputeNA[,2])  ), 
                    function(day){ if(day %in% c("“y—j“ú","“ú—j“ú") ){ "weekend" }
                                   else{"weekday"} 
                                  } ) )

data.imputeNA.weekday <- data.imputeNA[which(weekday.end=="weekday"), ]
data.imputeNA.weekend <- data.imputeNA[which(weekday.end=="weekend"), ]

intSteps.per.weekday <- tapply(data.imputeNA.weekday$steps, 
                               data.imputeNA.weekday$interval, 
                               mean)
intSteps.per.weekend <- tapply(data.imputeNA.weekend$steps, 
                               data.imputeNA.weekend$interval, 
                               mean)
plot( x=names(intSteps.per.weekday), 
      y=intSteps.per.weekday, main="weekday",
      type="l", xlab="interval", ylab="steps")

plot( x=names(intSteps.per.weekend), 
      y=intSteps.per.weekend, main="weekend",
      type="l", xlab="interval", ylab="steps")
```
